Index measures for oak decline severity using phenotypic descriptors

### 2020-02-09 manuscript/figures.Rmd
added explanation of descriptor importance plots

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures.'}
loadd(descriptor_contribution_plots)

>>>>

```{r descriptor_contributions, fig.height = 6,fig.cap = 'Descriptor mean decrease in accuracy importance scores from the random forest models $M_{PDI}$ and $M_{DAI}$ for relative contributions to the decline index measures. Descriptors are ordered by descending mean decrease in accuracy and therefore from highest contribution to lowest contribution to the given decline index.'}
loadd(descriptor_contribution_plots)

### 2020-02-09 manuscript/manuscript.Rmd
added explanation of descriptor importance plots

The top four ranked descriptors found to contribute to $M_{PDI}$ were all crown size and condition related descriptors with composite crown volume the top ranked descriptor overall (Figure 2a).
Other tree size related descriptors such as and live crown ratio stem bleeding descriptors contributed secondarily.

>>>>

The relative contributions of the phenotypic descriptors to the decline index models is shown in Figure 2.

The top four ranked descriptors found to contribute to $M_{PDI}$ were all crown size and condition related descriptors with composite crown volume the top ranked descriptor overall (Figure 2a).
Other tree size related descriptors such as bleed prevalence and live crown ratio stem bleeding descriptors contributed secondarily.
